DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-10-25 scnn.tex
changed affiliationg
filtering speed at multiple lmax

\address[SDSC]{Swiss Data Science Center (SDSC), Zurich, Switzerland}
\address[EPFL]{Institute of Electrical Engineering, EPFL, Lausanne, Switzerland}
\address[ETHZ]{Institute for Particle Physics and Astrophysics, ETHZ, Zurich, Switzerland}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{filtering_speed}
    \caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
    Both are executed on a single core.
	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.}
    \label{fig:filtering_speed}
\end{figure}

@@

Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
The cost of one such multiplication is $\bO(|\E| + |\V|)$.
By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations.
That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
That is especially true for smooth kernels which require a low polynomial degree $K$.
\figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.

>>>>

\address[SDSC]{Swiss Data Science Center (SDSC), Zurich, Switzerland}
\address[EPFL]{Institute of Electrical Engineering, EPFL, Lausanne, Switzerland}
\address[ETHZ]{Institute for Particle Physics and Astrophysics, ETH Zurich, Switzerland}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{filtering_speed}
    \caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function).
    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
    Both are executed on a single core.
	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.}
    \label{fig:filtering_speed}
\end{figure}

@@

Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
The cost of one such multiplication is $\bO(|\E| + |\V|)$.
By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations.
That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
That is especially true for smooth kernels which require a low polynomial degree $K$.
\figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
